### 2008-05-15 trunk/Papers/dl-gre-08/discussion.tex
autoren rein

\begin{figure}
\begin{center}
\includegraphics[width=0.25\textwidth]{drawers.png}
\end{center}\vspace*{-3ex}
\caption{A schematic view of the filing cabinets.}\label{fig:drawers}\vspace*{-3ex}
\end{figure}

@@

To evaluate the relational case, we first removed the
$\mathsf{column}$ and $\mathsf{row}$ predicates from the domain,
because these predicates make it possible to uniquely identify each
drawer with non-relational descriptions, and our algorithm would
always prefer these.  Using three (of the 240 possible) different
orderings, our algorithm was able to generate 10 of the 15
human-produced relational descriptions correctly.  This is shown in
more detail in Fig.~\ref{fig:example_outputs}; notice that four of the
15 descriptions occurred twice in the corpus.  Of the five
human-produced descriptions that the \el\ algorithm cannot generate,
two mention column information, which we excluded from our domain, and
three involve references to sets (\textit{the two blues ones in
  horizontal sequence}/\textit{the two yellow drawers}). While our
algorithm cannot reproduce those descriptions, it does generate other,
simpler descriptions for them.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.2\textwidth]{drawers.png}
\end{center}\vspace*{-3ex}
\caption{A schematic view of the filing cabinets.}\label{fig:drawers}\vspace*{-3ex}
\end{figure}

@@

%To evaluate the relational case, we first removed the
%$\mathsf{column}$ and $\mathsf{row}$ predicates from the domain,
%because these predicates make it possible to uniquely identify each
%drawer with non-relational descriptions, and our algorithm would
%always prefer these.  Using three (of the 240 possible) different
%orderings, our algorithm was able to generate 10 of the 15
%human-produced relational descriptions correctly.  This is shown in
%more detail in Fig.~\ref{fig:example_outputs}; notice that four of the
%15 descriptions occurred twice in the corpus.

When we add relations, our algorithm is able to generate 10 of the 15
human-produced relational descriptions correctly (in addition to the
98 non-relational descriptions). This is shown in more detail in
Fig.~\ref{fig:example_outputs}, which gives example outputs of the
\el\ algorithm for three different orderings. (Notice that four of the
15 descriptions occurred twice in the corpus.) Of the five
human-produced descriptions that the \el\ algorithm cannot generate,
three involve references to sets (\textit{the two blues ones in
  horizontal sequence}/\textit{the two yellow drawers}), and two
contain so much redundant information that our algorithm, which stops
once it has found a distinguishing description, cannot
reproduce it. While the
algorithm cannot reproduce those descriptions, it does generate other,
simpler descriptions for them.

%two mention column information, which we excluded from our domain, and
